Does language control differ between younger and older adults when switching

### 2023-05-30 manuscriptINSPIRE.Rmd
Fixed a typo

We analysed age-group differences for each task separately, with one analysis focusing on switching cost (switch and non-switch trials only) and one analysis on mixing costs (non-switch and single-rule trials). Accuracy was not at ceiling and analysed using generalized linear mixed-effects models. RTs were analysed through linear mixed-effects models, using package *lme4* (version `r packageVersion('lme4')`) and *lmerTEST* (version `r packageVersion('lmerTEST')`) in R (version `r paste0(R.Version()$major,'.', R.Version()$minor)`).

>>>>

We analysed age-group differences for each task separately, with one analysis focusing on switching cost (switch and non-switch trials only) and one analysis on mixing costs (non-switch and single-rule trials). Accuracy was not at ceiling and analysed using generalized linear mixed-effects models. RTs were analysed through linear mixed-effects models, using package *lme4* (version `r packageVersion('lme4')`) and *lmerTEST* (version `r packageVersion('lmerTest')`) in R (version `r paste0(R.Version()$major,'.', R.Version()$minor)`).
